References

### 2015-02-09 cv/XieXiaolei-Analyst.tex
Added two cover letters.

\section*{Education}
\begin{itemize}
\item Ph.D of Financial Mathematics, October 2014 - present
  \begin{itemize}
    \item {\it Reseach Areas:} I am mainly interested in the
      determination of the largest eigenvalues of a covariance matrix
      built from samples with heavy-tails. The purpose is dimension
      reduction, by which the behaviour of a diverse portfolio is
      replicated by one with much few components and hence analysis of
      the portfolio becomes more simplified and focused.

@@

\item Master of Physics, Lund University, January 2011 - June 2014
  \begin{itemize}
  \item {\it Major Subject:} Econophysics. In my thesis I studied the
    average eigenvalue distribution of sample covariance matrices,
    with a focus on the impact of autocorrelations and heavy tails.

    % The returns' models are fitted to such Swedish stocks as Volvo B,
    % Ericsson B, and Nordea Bank, using both publicly available daily
    % statistics and intra-day transaction data that I have been
    % collecting using home-developed software.

    % The studies are carried out analytically wherever feasible, and
    % otherwise by approximation and simulation. The application of
    % probability theories, random matrices, and stochastic processes
    % are the most involved subjects.
  \end{itemize}

@@

  My main responsibility is software development in C, and sometimes
  C++ and Java, in the Linux operating system.

@@

\section*{Private Project}
{\it Trade data collector and analyzer}
With this home-developed software I have been collecting intra-day
transaction data and analyzing them in real-time with Matlab. I make
heavy use of the Matlab economitrics toolbox with its built-in
routines for estimating ARIMA and GARCH models and then forecasting
using the obtained model. The idea is to pre-estimate a model and thus
fix its structure, such as the distribution of the residuals, the
order of the auto-regressive and the moving-average components, the
order of differencing/fractional differencing, etc., and then to 
evolve the model parameters in real-time as new data are fed into
the system.
\end{document}

>>>>

\section*{My Goal}
A self-funded Ph.D student of Finance \& Insurance mathematics
at KU, who is very experienced in programming and statistical analysis, is
looking for a part-time job as a quantitative analyst.

\section*{Education}
\begin{itemize}
\item Ph.D of Finance \& Insurance Mathematics, October 2014 - present
  \begin{itemize}
    \item {\it Reseach Areas:} I am mainly interested in the
      determination of the largest eigenvalues of a covariance matrix
      of samples with heavy-tails. The purpose is dimension
      reduction, by which the behaviour of a diverse portfolio is
      replicated by one with much few components and hence analysis of
      the portfolio becomes more simplified and focused.

@@

\item Master of Mathematical Physics, Lund University, January 2011 -
  June 2014
  \begin{itemize}
  \item {\it Major Subject:} Econophysics. In my thesis I studied the
    average eigenvalue distribution of sample covariance matrices,
    with a focus on the impact of autocorrelations and heavy tails.

    The volatility models were fitted to such Swedish stocks as Volvo B,
    Ericsson B, and Nordea Bank, using both publicly available daily
    statistics and intra-day transaction data that I had collected
    using home-developed software.

    The studies were carried out analytically wherever feasible, and
    otherwise by approximation and simulation. Software such as Maple,
    Mathematica and Matlab were used extensively.
  \end{itemize}

@@

  My main responsibility was software development in C, and sometimes
  C++ and Java, in the Linux operating system.

@@

\section*{Language Skills}
\begin{itemize}
\item English: Fluent
\item Swedish: Fairly good
\item Danish: Beginner
\end{itemize}

% \section*{Private Project}
% {\it Trade data collector and analyzer}
% With this home-developed software I have been collecting intra-day
% transaction data and analyzing them in real-time with Matlab. I make
% heavy use of the Matlab economitrics toolbox with its built-in
% routines for estimating ARIMA and GARCH models and then forecasting
% using the obtained model. The idea is to pre-estimate a model and thus
% fix its structure, such as the distribution of the residuals, the
% order of the auto-regressive and the moving-average components, the
% order of differencing/fractional differencing, etc., and then to 
% evolve the model parameters in real-time as new data are fed into
% the system.
\end{document}
